% !TEX root = ../main.tex

\section{Extension 1: Dynamic Misspecification (3-4 pages)}

\subsection{Simulation Design}

Extension~1 examines 
whether the finite-sample MSE ranking between LP(4) and the complexity-adjusted 
VAR sweep is robust to dynamic misspecification of the Wold representation. The 
baseline VAR(4) is augmented by a first-order moving average component, yielding 
a VARMA(4,1) DGP:

\begin{equation}
    y_t = A_1 y_{t-1} + A_2 y_{t-2} + A_3 y_{t-3} + A_4 y_{t-4} 
    + u_t + \Theta u_{t-1}, \quad u_t = B\varepsilon_t, \quad 
    \varepsilon_t \overset{\text{iid}}{\sim} \mathcal{N}(0, I_2)
\end{equation}

where $\Theta = \theta I_2$ is a scalar-scaled MA impact matrix, with 
misspecification strength $\theta \in \{0.1, 0.3, 0.6\}$. The case $\theta = 0$ 
nests back to the baseline VAR(4), ensuring continuity across designs. The VAR 
coefficient matrices $A_1, \ldots, A_4$ and the impact matrix $B$ are inherited 
from the baseline DGP, so that all variation across Extension~1 scenarios is 
attributable exclusively to the MA component.

The VARMA(4,1) DGP is invertible for all $\theta \in \{0.1, 0.3, 0.6\}$, 
admitting an infinite-order VAR representation. This means the complexity-adjusted 
VAR sweep retains its theoretical motivation: higher-order VAR$(q)$ specifications 
progressively approximate the true dynamics as $q \to \infty$, though at the cost 
of increasing parameter proliferation in finite samples. The central question is 
therefore whether LP(4) --- which is robust to this misspecification by virtue of 
its zero asymptotic bias \parencite{olea2025local} --- retains its MSE 
advantage over the equal-lag VAR(4), and where on the complexity-adjusted VAR 
frontier it sits relative to the baseline.

Persistence is varied across $\rho \in (0.5, 0.95)$ as in the baseline, 
since the degree to which the MA component distorts finite-sample VAR 
approximations depends directly on the persistence of the underlying process: 
at high $\rho$, shocks decay slowly and the MA term remains influential at 
longer horizons, amplifying the VAR's approximation bias. Sample sizes follow 
the baseline design, $T \in \{100, 200, 240, 500\}$. The misspecification 
strength $\theta \in \{0.1, 0.3, 0.6\}$ is thus varied jointly with 
persistence and sample size, yielding a three-way design that isolates the 
marginal contribution of MA misspecification from the persistence and 
finite-sample channels already documented in the baseline.

The structural estimand $\theta_h = \Psi_h^{\mathrm{VARMA}} B e_1$ is defined 
with respect to the true VARMA moving-average matrices $\Psi_h^{\mathrm{VARMA}}$, 
computed analytically from the VARMA companion representation prior to each 
simulation run. Both estimators --- LP(4) and the VAR$(q)$ sweep --- are applied 
without modification to the VARMA-generated data, so that the misspecification 
is fully absorbed into the finite-sample performance of each estimator rather 
than accommodated by the estimation procedure. Performance measures are identical 
to the baseline.

\subsection{Simulation Results}


