% !TEX root = ../main.tex

\section{Extension 2: Functional Misspecification (3-4 pages)}

\subsection{Simulation Design}

Extension~2 examines 
whether the finite-sample MSE ranking between LP(4) and the complexity-adjusted 
VAR sweep is robust to functional misspecification of the DGP. The baseline 
VAR(4) is augmented by a quadratic term in the first structural shock, yielding 
a nonlinear DGP:

\begin{equation}
    y_t = A_1 y_{t-1} + A_2 y_{t-2} + A_3 y_{t-3} + A_4 y_{t-4} 
    + u_t + \gamma \cdot c(\varepsilon_{1,t}), \quad u_t = B\varepsilon_t, 
    \quad \varepsilon_t \overset{\text{iid}}{\sim} \mathcal{N}(0, I_2)
\end{equation}

where $c(\varepsilon_{1,t}) = (0,\ \varepsilon_{1,t}^2 - 1)'$ is a 
mean-zero quadratic term in the first structural shock entering the second 
equation only, and $\gamma \in \{0.3, 0.6\}$ controls the degree of 
nonlinearity. The centering $\varepsilon_{1,t}^2 - 1$ ensures that the 
nonlinear term has mean zero, so that $\gamma = 0$ nests back to the 
baseline VAR(4).

This shock-quadratic specification is adopted in place of a level-quadratic 
or lag-quadratic formulation for two reasons. First, a quadratic term in 
lagged levels introduces positive feedback into the system dynamics and is 
explosive for moderate values of $\gamma$, violating the covariance 
stationarity required for the estimand $\theta_h$ to be well-defined. 
Second, and more importantly, a quadratic term in the structural shock 
isolates the nonlinearity in the transmission mechanism rather than in the 
propagation dynamics. This distinction matters for the research question: 
since the Cholesky-identified structural shock $\varepsilon_{1,t}$ enters 
the system linearly in the baseline VAR(4), a shock-quadratic extension 
targets precisely the channel emphasized by \textcite{plagborg2021local} 
--- namely, that linear LP and linear VAR are both blind to nonlinearities 
in the shock transmission in population (Proposition~1, p.~960). A 
lag-quadratic specification would instead distort the propagation dynamics 
and complicate the identification of the structural shock, confounding the 
comparison with the baseline DGP. The shock-quadratic formulation thus 
provides the cleanest test of whether the complexity-adjusted VAR sweep 
offers any finite-sample advantage when functional misspecification is 
present but structurally uninvertible --- that is, not approximable by 
higher-order linear VARs regardless of lag length.

The key theoretical motivation for this extension follows from 
\textcite{plagborg2021local}, who establish that linear LP and linear VAR 
estimate the same best linear approximation to the true IRF in population, 
regardless of whether the DGP is linear (Proposition~1, p.~960). Under 
equal lag length, both estimators are therefore equally blind to the 
quadratic misspecification in population, and any finite-sample divergence 
reflects differences in the bias-variance tradeoff and the inference channel 
rather than differential robustness to nonlinearity per se. This makes 
Extension~2 complementary to Extension~1: whereas Extension~1 isolates the 
bias channel under invertible dynamic misspecification, Extension~2 isolates 
the inference channel, since the nonlinear DGP generates non-Gaussian and 
serially dependent Wold innovations that affect the finite-sample coverage 
of LP and VAR differently. Critically, unlike the VARMA misspecification in 
Extension~1, the quadratic term is not approximable by higher-order linear 
VARs, which implies that the complexity-adjusted VAR sweep has no 
approximation advantage over VAR(4) in this setting.

The structural estimand is the best linear approximation to the true 
nonlinear IRF, $\theta_h^{\mathrm{lin}} = \Psi_h B e_1$, where $\Psi_h$ 
and $B$ are defined with respect to the linear component of the DGP. Since 
both LP and VAR target this same linear estimand in population 
\parencite{plagborg2021local}, the comparison remains well-defined under 
nonlinear misspecification. Persistence is varied across $\rho \in (0.5, 
0.95)$ as in the baseline and Extension~1, and sample sizes follow the 
baseline design $T \in \{100, 200, 240, 500\}$. The nonlinearity strength 
$\gamma \in \{0.3, 0.6\}$ is varied jointly with persistence and sample 
size. Both estimators are applied without modification to the 
nonlinearity-generated data, so that the misspecification is fully absorbed 
into the finite-sample performance of each estimator. Performance measures 
are identical to the baseline.
\subsection{Simulation Results}


