% !TEX root = ../main.tex

% INTRODUCTION PATRICK

\section{Introduction}


To infer statements about the dynamic response to exogenous shocks, the estimation of 
the corresponding impulse response has relied on two fundamental approaches, either 
through vector autoregressive (VAR) or Local Projection (LP) models. Since the 
introduction of the latter, an extensive literature has emerged discussing the relative 
merits of the two. A first strand of literature has established that, under relatively 
general conditions, LPs and VARs estimate the same population impulse responses 
\parencite{plagborg2021local, fusari2026more}. However, in the discussion of finite-sample 
behavior based on equal lag lengths, LPs were often viewed as less sensitive to dynamic misspecification 
\parencite{jorda2005estimation, ramey2016macroeconomic}, a property that \textcite{olea2024double} 
subsequently formalise, whereas VARs were seen as potentially more statistically 
efficient \parencite{li2024local, olea2025local}. \textcite{ludwig2026local} offers an 
analytical explanation of the observed finite-sample bias-variance tradeoff. He shows 
that LPs can be represented as a sequence of VAR estimations increasing in lag length 
as the estimated horizon increases, and thus argues for a renewed thinking about how 
we can compare LPs and VARs, not by lag length, but by effective complexity.

Our paper aims to answer two questions. First, under correct specification, where does a fixed 
LP estimator sit relative to the full complexity-adjusted VAR frontier, and does the 
conventional equal-lag ranking survive once that frontier is made visible? Second, once 
controlled dynamic misspecification is introduced, does any genuine LP advantage 
emerge, and if so, does it manifest in point estimation, in inference, or both?

The first part of this paper operationalizes \textcite{ludwig2026local}'s central 
implication through a complexity-adjusted benchmarking exercise in which a fixed LP(4) 
estimator is compared to progressively higher-order VAR specifications that proxy 
increasing effective dynamic flexibility \parencite{de2025long}. This comparison is 
conducted across empirically relevant sample sizes \parencite[see e.g.][]{herbst2024bias} 
to assess how the resulting bias-variance tradeoff depends on the available data.

The second part introduces controlled dynamic misspecification. While the baseline 
experiment studies complexity-adjusted LP-VAR comparisons under correctly specified 
linear dynamics, the main practical argument for LPs concerns their robustness when 
the estimated linear model is only an approximation to the true DGP 
\parencite{montiel2021local,olea2024double}. To study this channel explicitly, the paper augments 
the baseline VAR(4) with a moving-average component, yielding a VARMA(4,1) DGP, 
and examines how the relative performance of LP(4), equal-lag VAR(4), and higher-order 
VARs changes as the degree of dynamic misspecification increases.

For each estimator, horizon, DGP, and sample size, we compute bias, variance, mean 
squared error, and empirical coverage rates. Bias and variance describe the 
finite-sample tradeoff in point estimation, while coverage assesses whether the 
corresponding inference procedures remain reliable under increasing dynamic 
misspecification.

Our findings suggest that under correct specification, the conventional point-estimation advantage of equal-lag Vector Autoregressions VARs persists, but this superiority is largely an artifact of mismatched model complexities. By locating a fixed $LP(4)$ estimator on the complexity-adjusted VAR frontier, we reveal that it operates inherently at the level of a highly parameterized system, intersecting the VAR sweep at orders higher than $q \approx 15$. However, evaluating performance solely through point estimation obscures a critical divergence in inference. Local projections  maintain robust, near-nominal coverage across all persistence regimes, whereas the parametric efficiency of VARs comes at the cost of severe inferential fragility, leading to dramatic under-coverage near the unit root boundary. 

When controlled dynamic misspecification is introduced via a VARMA$(4,1)$ data-generating process, a genuine LP advantage emerges in terms of inferential stability rather than point estimation. While the absolute root mean squared error of the LP estimator increases under misspecification, its intersection with the complexity frontier shifts visibly leftward. This indicates that the LP(4) becomes algebraically equivalent to a progressively more parsimonious VAR representation, thereby increasing its relative efficiency against the class of low-order VARs. Despite this relative shift, the equal-lag VAR(4) continues to strictly dominate the LP(4) reference line in finite-sample point estimation. The true merit of the direct projection method under dynamic misspecification lies in its robustness of inference; it preserves stable, near-nominal confidence interval coverage across persistence regimes, while the coverage of analytical VAR delta-method intervals substantially deteriorates.

The remainder of the paper is structured as follows. Section 2 provides a theoretical overview of vector autoregressions and local projections. It also reviews the empirical literature regarding their bias-variance trade-off at equal lag lengths and discusses their asymptotic and finite-sample equivalence. Section 3 presents our baseline simulation study under correct specification. Section 4 extends this framework by introducing dynamic misspecification. Section 5 concludes.

\FloatBarrier