% !TEX root = ../main_ext_1.tex

\section{Theoretical Background}

An impulse response measures how an outcome reacts over time to a single shock.
Following \textcite{koop1996impulse}, it can be defined nonparametrically as the
difference between two forecasts of $y_{t+h}$. Both forecasts use the same controls
$\mathbf{x}_t$ and differ only in the time-$t$ value of the variable of interest $s_t$.
One forecast sets $s_t = s_0 + \delta$, raising the baseline $s_0$ by a shock of size
$\delta$, while the other is kept at $s_0$. The controls $\mathbf{x}_t$ hold fixed the
information used to identify the response, namely the lags of the system and, under some
identification schemes, contemporaneous variables. Following \textcite{ramey2016macroeconomic},
a shock is an exogenous and unanticipated movement that is uncorrelated with the controls in
$\mathbf{x}_t$ and with all other structural shocks. At horizon $h$, the gap between the two
forecast paths is the causal effect of the shock in population,
%
\begin{equation}
    IR(h,\delta) \equiv
    \mathbb{E}\!\left[\,y_{t+h} \mid s_t = s_0 + \delta;\, \mathbf{x}_t\right]
    - \mathbb{E}\!\left[\,y_{t+h} \mid s_t = s_0;\, \mathbf{x}_t\right].
    \label{eq:EF_IRF}
\end{equation}
%
Vector autoregressions and local projections are the two standard ways to estimate this
object in finite samples. A VAR, introduced by \textcite{sims1980macroeconomics}, fits the
joint dynamics of all variables as one autoregressive system and reads impulse responses off
the estimated model by iterating it forward. A local projection, introduced by
\textcite{jorda2005estimation}, instead estimates the response at each horizon with its own
OLS regression of the future outcome on current and past data. Because they build the response differently, the two estimators accumulate estimation error in different ways across
horizons. At an equal lag order they sit at opposite ends of a bias-variance spectrum, with
local projections carrying more variance and VARs more bias under misspecification
\parencites{li2024local}{olea2025local}. \textcite{ludwig2026local} argues that this
equal-order comparison is misleading, because at a given lag order $p$ an LP$(p)$ is strictly
more flexible than a VAR$(p)$. The usual bias-variance trade-off therefore mixes the choice of
estimator with the choice of model complexity.

\subsection{Introduction to VARS}
Following \textcite{lutkepohl2005}, we define a VAR($p$) population model in which the
outcome of interest $y_t$ is a $K \times 1$ random vector, the $A_i$ are fixed $K \times K$
coefficient matrices, and $u_t$ is $K$-dimensional white noise with $\mathbb{E}\left[ u_t\right] = 0$,
a nonsingular covariance matrix $\mathbb{E}\left[ u_t u_t' \right] = \Sigma_u$, and
$\mathbb{E}\left[ u_t u_s' \right] = 0$ for $t \neq s$. Rather than write out all $p$ lags, we
cast the VAR($p$) in its equivalent VAR(1) companion form,
%
\begin{equation}
    Y_t =\mathbf{\nu} + \mathbf{A} Y_{t-1} + U_t
\end{equation}
%
where
%
\begin{equation*}
\mathbf{\nu} := \underset{Kp\times 1}{\begin{bmatrix} \nu \\ 0 \\ \vdots \\ 0 \end{bmatrix}}, \quad
Y_t := \underset{Kp\times 1}{\begin{bmatrix} y_t \\ y_{t-1} \\ \vdots \\ y_{t-p+1} \end{bmatrix}}, \quad
\mathbf{A} := \underset{Kp\times Kp}{\begin{bmatrix}
A_1 & A_2 & \cdots & A_{p-1} & A_p \\
I_K & 0   & \cdots & 0       & 0   \\
0   & I_K &        & 0       & 0   \\
\vdots & & \ddots & & \vdots \\
0   & 0   & \cdots & I_K     & 0
\end{bmatrix}}, \quad
U_t := \underset{Kp\times 1}{\begin{bmatrix} u_t \\ 0 \\ \vdots \\ 0 \end{bmatrix}}.
\end{equation*}
%
If $Y_t$ satisfies the stability condition, so that all roots $z$ of the characteristic
equation lie strictly outside the unit circle, the process is covariance stationary and admits
a Wold moving-average (MA) representation
%
\begin{equation}
\det(I_{Kp} - \mathbf{A}z) \neq 0 \text{ for } |z| \le 1 \iff Y_t = \mathbf{\mu} +
\sum_{\ell=0}^{\infty}\mathbf{A}^{l}U_{t-\ell}, \qquad \text{where }\mathbf{\mu} := \mathbb{E}(Y_t)
\end{equation}
%
Keeping only the top $K$ rows gives the moving-average representation for $y_t$
%
\begin{equation}
    y_t = \mu + \sum_{\ell=0}^{\infty} \Psi_\ell\, u_{t-\ell},
\qquad \Psi_\ell := [\mathbf{A}^\ell]_{1:K,\,1:K}
    \label{eq:wold_yt}
\end{equation}
%
where $\Psi_h$ is the reduced-form impulse response at horizon $h$, the response of $y_{t+h}$
to a reduced-form innovation $u_t$. It is the upper-left $K \times K$ block of $\mathbf{A}^h$,
because $U_{t-\ell} = (u_{t-\ell}, 0, \ldots, 0)'$ is nonzero only in its first $K$ positions.
The components of $u_t$ are generally correlated at the same date,
$\Sigma_u = \mathbb{E}(u_t u_t') \neq I_K$, so a shock to one component moves the others
contemporaneously. The reduced-form responses $\Psi_h$ therefore carry no structural
interpretation. To identify structural shocks, we restrict the impact matrix $B$ in
$u_t = B\varepsilon_t$, where $\varepsilon_t \sim (0, I_K)$ are mutually uncorrelated structural
shocks and $\Sigma_u = BB'$.

The most common choice is recursive Cholesky identification \parencite{ramey2016macroeconomic},
which makes $B$ lower triangular with positive diagonal entries and so recovers it uniquely as
the Cholesky factor of $\Sigma_u$. The ordering imposes a causal structure, as the variable
ordered first responds contemporaneously to all shocks while the variable ordered last is
insulated from all contemporaneous feedback. The diagonal entries $b_{ii}$, $i = 1, \ldots, K$,
measure the direct impact of structural shock $i$ on variable $i$, and the off-diagonal entries
$b_{ij}$, $1 \leq j < i \leq K$, capture the contemporaneous spillover from shock $j$ to variable
$i$. Substituting $u_t = B\varepsilon_t$ into \eqref{eq:wold_yt} yields the structural
moving-average representation
%
\begin{equation}
    y_t = \mu + \sum_{\ell=0}^{\infty} \Theta_\ell\, \varepsilon_{t-\ell},
\qquad \Theta_\ell := \Psi_\ell B,
    \qquad B = \begin{pmatrix}
b_{11} & 0      & \cdots & 0      \\
b_{21} & b_{22} & \cdots & 0      \\
\vdots &        & \ddots & \vdots \\
b_{K1} & b_{K2} & \cdots & b_{KK}
\end{pmatrix}
    \label{eq:sma}
\end{equation}
%
where the $(i,j)$-th element of $\Theta_h$ is the response of variable $i$ to a unit innovation
in shock $j$ at horizon $h$. The structural impulse response of variable $i$ to shock $j$ is thus
%
\begin{equation}
    \theta_h^{ij} = [\Psi_h B]_{ij}
    \label{eq:sirf}
\end{equation}
%
where $[\,\cdot\,]_{ij}$ denotes the $(i,j)$-th element of a matrix. Leading \eqref{eq:sma}
forward by $h$ periods gives
%
\begin{equation}
    y_{t+h} = \mu + \sum_{\ell=0}^{\infty} \Theta_\ell\, \varepsilon_{t+h-\ell}.
    \label{eq:sma_forward}
\end{equation}
%
Because the structural shocks are mutually and serially uncorrelated, with
$\varepsilon_t \sim (0, I_K)$, projecting $y_{t+h}$ on the date-$t$ shock $\varepsilon_t$ keeps
only the $\ell = h$ term, since all leads and lags are orthogonal to $\varepsilon_t$. The
response of variable $i$ to a unit innovation in shock $j$ at horizon $h$ is therefore
%
\begin{equation}
\theta_h^{ij}
= \frac{\partial\, \mathbb{E}\!\left[y_{i,t+h} \mid \varepsilon_{j,t}\right]}
       {\partial\, \varepsilon_{j,t}}
= [\Theta_h]_{ij} = [\Psi_h B]_{ij},
\end{equation}
%
which is exactly the population object $\mathrm{IR}(h,\delta)$ of Equation \eqref{eq:EF_IRF},
specialised to a unit structural innovation in shock $j$.

Estimation of the structural impulse response $\hat{\theta}_h^{ij}$ proceeds in two stages. In
the first, the stacked coefficient matrix $A := [A_1, \ldots, A_p]$ of dimension $K \times Kp$ is
estimated equation by equation via OLS. If the process satisfies the stability condition and the
innovations $u_t$ form a strictly stationary martingale difference sequence with positive definite
covariance and finite fourth moments, this estimator is asymptotically normal
\parencite{hansen2022econometrics},
%
\begin{equation}
    \sqrt{T}\,\bigl(\mathrm{vec}(\hat{A}) - \mathrm{vec}(A)\bigr)
    \xrightarrow{d} \mathcal{N}\!\left(0,\; V_{\alpha}\right),
\end{equation}
%
where the asymptotic covariance takes the robust sandwich form
$V_{\alpha} = \overline{\Gamma}^{-1} \Omega \overline{\Gamma}^{-1}$. Here
$\overline{\Gamma} = I_K \otimes \Gamma$, with $\Gamma = \mathbb{E}(Z_t Z_t')$ the second-moment
matrix of the stacked regressors $Z_t = (1, y_{t-1}', \ldots, y_{t-p}')'$, and
$\Omega = \mathbb{E}(u_t u_t' \otimes Z_t Z_t')$. Under conditional homoskedasticity, $\Omega$
simplifies to $\Sigma_u \otimes \Gamma$ and the asymptotic variance reduces to the standard form
$\Gamma^{-1} \otimes \Sigma_u$ \parencite{lutkepohl2005}, where OLS is asymptotically efficient.
The general form $V_{\alpha}$ remains necessary for valid inference when the data-generating
process is conditionally heteroskedastic.

In the second stage, the structural objects are recovered from the reduced-form estimates. The
impact matrix $\hat{B}$ is the Cholesky factor of $\hat{\Sigma}_u$, and the reduced-form impulse
responses follow from the recursion
%
\begin{equation}
    \hat{\Psi}_h = \sum_{\ell=1}^{\min(h,p)} \hat{A}_\ell\,\hat{\Psi}_{h-\ell},
    \qquad \hat{\Psi}_0 = I_K.
    \label{eq:var_wold_recursion}
\end{equation}
%
so that the structural impulse response estimator $\hat{\theta}_h^{ij} = g(\hat{\alpha}, \hat{\sigma})$,
with $\alpha = \mathrm{vec}(A)$ and $\sigma = \mathrm{vec}(\Sigma_u)$, is a smooth nonlinear
function of the first-stage estimates,
%
\begin{equation}
    \hat{\theta}_h^{ij} = \bigl[\hat{\Psi}_h\,\hat{B}\bigr]_{ij}.
    \label{eq:var_srf_estimator}
\end{equation}
%
Since $g$ is differentiable in $(\hat{\alpha}, \hat{\sigma})$, the delta method gives
%
\begin{equation}
    \sqrt{T}\,\bigl(\hat{\theta}_h^{ij} - \theta_h^{ij}\bigr)
    \xrightarrow{d}
    \mathcal{N}\!\left(0,\;
    \nabla g(\alpha,\sigma)'\,\Sigma_{\alpha,\sigma}\,\nabla g(\alpha,\sigma)
    \right),
    \label{eq:var_delta_method}
\end{equation}
%
where $\Sigma_{\alpha,\sigma}$ is the joint asymptotic covariance of $(\hat{\alpha}', \hat{\sigma}')'$
and the Jacobian $\nabla g(\alpha, \sigma)$ has a closed-form expression
\parencite{lutkepohl1990asymptotic}. These confidence intervals are valid pointwise in $h$ under
stationarity, but not uniformly over the persistence of the process or over growing horizons,
which motivates a direct look at finite-sample behaviour.

These favourable asymptotic properties are qualified by three related problems at the sample sizes
typical of macroeconomic work. First, estimation error propagates through iteration. Because
$\hat{\Psi}_h$ is the upper-left block of $\hat{\mathbf{A}}^h$, error in $\hat{A}$ enters the
impulse response through powers of the companion matrix and compounds as the horizon grows. Even
small coefficient biases then translate into large distortions at longer horizons
\parencite{kilian1998small}. With unit or near-unit roots, \textcite{phillips1998impulse} shows
that long-horizon responses from unrestricted VARs are not even consistently estimated, converging
to random variables rather than the true responses.

Second, the autoregressive coefficients are biased downward in short samples, as least squares
underestimates the persistence of the process
\parencites{marriott1954bias}{nicholls1988bias}{pope1990biases}. Because $\hat{\Psi}_h$ inherits
this bias through the recursion, the estimated responses decay too quickly and understate the true
persistence. The distortion is worst when persistence is high and the sample is short.

Third, these distortions undermine delta-method inference. As the largest roots approach the unit
circle, the normal approximation deteriorates and the confidence intervals undercover, increasingly
so at longer horizons \parencites{kilian1998small}{kilian1999finite}.

A further class of distortions arises when the autoregressive structure is itself misspecified. If
the true process has moving-average components, a finite-order VAR is generically inconsistent
regardless of sample size, and although higher-order approximations can asymptotically absorb the
omitted MA dynamics, the required lag expansion quickly exhausts degrees of freedom in samples of
typical macroeconomic length \parencite{braun1993misspecifications}. The consequences of lag choice
are also asymmetric. Overfitting only inflates variance, whereas underfitting omits higher-order
dynamics of the response and produces spuriously tight intervals with coverage far below nominal
\parencite{kilian2001impulse}. Both channels are population-level phenomena.
\textcite{ravenna2007vector} shows that truncation bias in the VAR coefficients, and the resulting
contamination of the structural rotation matrix, persists even as $T \to \infty$.

\subsection{Introduction to Local Projections}

Whereas the VAR recovers the impulse response by iterating a single fitted model forward, the
local projection estimates each horizon directly from its own regression
\parencite{jorda2005estimation}. Following \textcite{jorda2025local}, the LP obtains the
horizon-$h$ response of the outcome $y$ to the shock $s_t$ by projecting the future outcome
$y_{t+h}$ onto $s_t$ while controlling for the conditioning set $\mathbf{x}_t$ that spans the
information of the system,
%
\begin{equation}
    y_{t+h} = \alpha_h + \beta_h\, s_t
            + \boldsymbol{\gamma}_h'\, \mathbf{x}_t
            + \xi_{t+h}^{(h)},
    \qquad h = 0, 1, \ldots, H,
    \label{eq:lp_shock}
\end{equation}
%
where $y_{t+h}$ is the scalar response and $s_t$ the scalar shock of interest, which for an
observed structural innovation is $s_t = \varepsilon_{j,t}$. The control vector
$\mathbf{x}_t = (y_{t-1}', \ldots, y_{t-p}')'$ collects the $p$ lags that span the conditioning
information and, under non-recursive identification, may also include contemporaneous controls.
Here $\alpha_h$ is a constant that can be omitted without loss of generality,
$\boldsymbol{\gamma}_h$ a $(Kp \times 1)$ vector of coefficients on the controls, and
$\xi_{t+h}^{(h)}$ the horizon-$h$ projection residual. The leading coefficient $\beta_h$ is the
impulse response itself. When $y$ is variable $i$ and $s_t = \varepsilon_{j,t}$, it coincides with
the structural response $\theta_h^{ij}$ of Equation \eqref{eq:sirf} and with the population object
$\mathrm{IR}(h,\delta = 1)$ of Equation \eqref{eq:EF_IRF}.

Under appropriate identification, in the simplest case exogeneity of $s_t$ conditional on
$\mathbf{x}_t$, the impulse response is the OLS coefficient $\hat{\beta}_h$ on $s_t$ in
Equation \eqref{eq:lp_shock}. The LP thus recovers the response without parametrizing the
propagation dynamics, unlike the VAR, which relies on a fitted autoregressive model and forward
iteration. When conditional exogeneity fails, causal interpretation can instead be restored by
enriching $\mathbf{x}_t$ to achieve selection on observables \parencite{olea2025local}, by
instrumenting $s_t$ with an external proxy under a relevance and lead-lag exogeneity condition
\parencite{stock2018identification,jorda2015betting}, or by importing a conventional VAR
identification scheme such as the recursive Cholesky ordering \parencite{plagborg2021local}. The
instrumental-variable route is moreover robust to non-invertibility, recovering the response even
when the structural shock is not spanned by current and past observables and the recursive scheme
therefore fails.

Unlike the VAR, estimation of $\hat{\beta}_h$ proceeds in a single stage, directly by OLS on
Equation \eqref{eq:lp_shock}, whose leading coefficient is the horizon-$h$ impulse response
\parencite{jorda2025local}. Because $\hat{\beta}_h$ is the coefficient on a regressor that is
orthogonal to the projection error $\xi_{t+h}^{(h)}$ by construction of the structural shock, it
recovers the response without passing through a nonlinear mapping, and hence without the
delta-method step that governs the VAR estimator in Equation \eqref{eq:var_delta_method}.

Provided that the process $\{y_t\}$ is strictly stationary and ergodic, with a positive definite
covariance matrix, bounded moments $\mathbb{E}\lVert y_t \rVert^{r} < \infty$ for some $r > 4$, and
mixing coefficients satisfying $\sum_{\ell=1}^{\infty} \alpha(\ell)^{1-4/r} < \infty$, the
least-squares estimator is asymptotically normal \parencite{hansen2022econometrics}. Letting
$n = T - h$ denote the effective sample size at horizon $h$ and
$\mathbf{w}_t = (s_t, \mathbf{x}_t')'$ the stacked vector of all regressors, we have
%
\begin{equation}
    \sqrt{n}\,\bigl(\hat{\mathbf{b}}_h - \mathbf{b}_h\bigr)
    \xrightarrow{d} \mathcal{N}\!\left(\mathbf{0},\; V_h\right),
    \label{eq:lp_clt}
\end{equation}
%
where $\mathbf{b}_h = (\beta_h, \boldsymbol{\gamma}_h')'$ is the vector of all projection
coefficients and $\hat{\mathbf{b}}_h$ its OLS estimate. The asymptotic covariance matrix takes the
robust sandwich form
%
\begin{equation}
    V_h = Q^{-1} \Omega_h Q^{-1},
\end{equation}
%
where $Q = \mathbb{E}(\mathbf{w}_t \mathbf{w}_t')$ is the second-moment matrix of the regressors,
and $\Omega_h$ is the long-run variance matrix of the projection scores, defined as
%
\begin{equation}
    \Omega_h = \sum_{\ell=-\infty}^{\infty} \mathbb{E}\Bigl[\bigl(\xi_{t+h-\ell}^{(h)} \mathbf{w}_{t-\ell}\bigr) \bigl(\xi_{t+h}^{(h)} \mathbf{w}_t\bigr)'\Bigr].
\end{equation}
%
The long-run form of this covariance matrix reflects a basic feature of direct projection. Because
the predictive regression aggregates the shocks accruing between $t$ and $t+h$ over overlapping
forecast windows, the projection error $\xi_{t+h}^{(h)}$ follows a moving-average process of order
$h-1$ and is therefore serially correlated.

To illustrate this mechanism, consider the stylized AR(1) DGP of \textcite{jorda2025local}, with
persistence parameter $\rho$, initial condition $y_0 = 0$, and a strictly stationary error term
$u_t$ satisfying $\mathbb{E}[u_t|\{u_s\}_{s\neq t}] = 0$ almost surely
%
\begin{equation}
    y_t = \rho y_{t-1} + u_t.
\end{equation}
%
With the simplified local projection of Equation \eqref{eq:lp_shock}, the $h$-step regression is
%
\begin{equation}
    y_{t+h} = \beta_h\, y_t + \xi_{t+h}^{(h)}
    \label{eq:lp_ar1}
\end{equation}
%
and recursive substitution of the AR(1) law of motion into \eqref{eq:lp_ar1}, writing
$\beta(\rho, h)$ for the LP IRF estimator of $\rho^h$ and $\xi(\rho, h)$ for the corresponding
residual, yields
%
\begin{equation}
    y_{t+h} = \beta(\rho, h) y_t + \xi(\rho, h) , \qquad \xi(\rho, h) = \sum_{j=1}^{h} \rho^{h-j}\, u_{t+j}.
    \label{eq:ar1_recursive}
\end{equation}
%
The stronger the persistence $\rho$, the larger and more slowly decaying the autocovariances of
$\xi(\rho, h)$, which worsens the distortion in naive OLS standard errors. As $\rho \to 1$, OLS
also exhibits non-standard near-unit-root behaviour, invalidating inference based on standard
normal critical values. As long as $\rho$ lies safely inside the unit circle ($|\rho| < 1$),
however, the LP estimator is consistent, $\hat{\beta}_h \xrightarrow{p} \beta_h = \theta_h^{ij}$,
and remains asymptotically normal once the serially correlated residuals are appropriately
corrected \parencite{montiel2021local,jorda2025local}.

To address this serial correlation, \textcite{jorda2005estimation} originally proposed Newey-West
type \parencite{newey1987simple} heteroskedasticity- and autocorrelation-consistent (HAC) standard
errors. In practice, HAC inference brings its own complications. It requires tuning parameters with
complex interpretations \parencite{lazarus2018har} and can itself be a source of finite-sample
bias. \textcite{herbst2024bias} show that, although HAC estimators are asymptotically valid, the
long-run variance is typically downward-biased in short samples, which systematically understates
the uncertainty around the point estimate.

To allow valid inference even near unity, \textcite{montiel2021local} augment the local projection
with one additional lag. Under the weak assumption that the shock is unpredictable from its own past
and future, this makes the regression score, the product of the projection residual
$\xi^{(h)}_{t+h}$ and the regressor of interest after partialling out the controls, serially
uncorrelated. Conventional Eicker--Huber--White (EHW) heteroskedasticity-robust standard errors then
suffice despite the serially correlated residual. The resulting $t$-statistic is asymptotically
standard normal uniformly over $\rho \in [-1,1]$ and horizons $h/T \to 0$.

A long-standing piece of conventional wisdom holds that local projections are more robust to
misspecification than VARs, originating with \textcite[162]{jorda2005estimation} and echoed across
later surveys \parencite{ramey2016macroeconomic,li2024local}. \textcite{plagborg2021local} document
this view while noting that it had long lacked a formal foundation. In their finite-order treatment,
LPs are indeed generally more robust to misspecification than equal-order VARs, a property they
establish without invoking the population equivalence of the two estimands. \textcite{olea2024double}
show why. Because the LP reads each horizon off a separate regression rather than iterating a single
fitted model forward, a misspecification of the short-run dynamics does not compound through the
powers of the companion matrix as it does for the VAR, whose bias arises precisely from
extrapolating the response through the iterated mapping $\hat A^{h}$ that the misspecified model no
longer satisfies.

As with VARs, however, \textcite{herbst2024bias} show that LP point estimates are biased downward in
finite samples, for two reasons. First, and unlike VARs, the finite-sample estimation of the
intercept distorts the sample covariance between shock and outcome even when the two are uncorrelated
in population. Second, and as with VARs, the estimation of the lagged-variable coefficients inherits
the classical downward bias of least-squares autoregressive estimators \parencite{pope1990biases} and
grows the more persistent the controls are. Both channels make the bias depend on the true impulse
responses at neighbouring horizons and worsen with persistence and the horizon, as it accumulates
over an expanding sum of terms as $h$ increases. Although \textcite{herbst2024bias} propose a
bias-corrected estimator, \textcite{li2024local} find that it reduces bias only partially and at the
cost of higher variance.

\subsection{On the Equivalence of VARs and Local Projections}

As local projection inference gained popularity over the last decade, a growing body of
simulation evidence has compared the finite-sample performance of LP and VAR estimators across
data-generating processes of differing richness. Two findings recur. When the DGP admits an exact
finite-order VAR representation, the VAR is correctly specified at the true lag order, dominates LP
on mean-squared-error criteria at intermediate and long horizons, and is thus the preferable choice
for point estimation \parencite{olea2024double,li2024local}. On coverage, \textcite{kilian2011reliable}
and \textcite{brugnolini2018local} show that LP intervals are less accurate than an equivalent VAR
benchmark. Although this largely reflects the standard error chosen for the local projection,
\textcite{olea2024double} find no LP advantage even when switching from HAC to EHW standard errors.
The added flexibility of least-squares LP therefore yields little bias reduction over the already
well-specified VAR, while carrying substantially higher variance.

When the DGP departs from any finite-order VAR, however, as in the empirically calibrated dynamic
factor models of \textcite{li2024local} or under an extension to VARMA processes, a genuine
bias-variance trade-off emerges. Here the least-squares LP has lower bias than the VAR but
substantially higher variance at intermediate and long horizons, so VAR methods remain preferable
under MSE unless researchers place a higher weight on bias reduction \parencite{li2024local}. On
coverage, \textcite{olea2024double} show that LPs with EHW inference yield correctly centred
intervals, whereas VARs severely undercover and their bias leaves the intervals off-centre. For lag
truncation, \textcite{brugnolini2018local} varies the common lag length of LPs and VARs against a
true VAR(12) process and shows that LP coverage improves relative to VARs as the gap to the true lag
length widens.

All these simulation studies, however, compare LPs and VARs at a single common lag length $p$, a
design that presupposes the two methods estimate the same object. \textcite{plagborg2021local}
establish that, under weak stationarity, an unrestricted lag structure, and a common identification
scheme, the LP and VAR estimators converge to the identical structural impulse response function in
population, up to a constant of proportionality. Any conventional LP impulse response can therefore
be obtained from an appropriately ordered recursive VAR, and vice versa. Moreover, because both
methods act as best linear predictors of the data-generating process, the authors show that they are
symmetrically robust to nonlinear misspecification in population.

Crucially for the equal-lag designs above, \textcite{plagborg2021local} further show that when both
specifications are fixed at order $p$, their population estimands agree exactly up to horizon
$h \le p$ but generally diverge for $h > p$. The divergence is thus localized to horizons beyond the
estimation lag length, precisely the intermediate and long horizons where the simulation literature
finds the bias-variance trade-off most pronounced. In practice, then, LP versus VAR is not a choice
between different population objects but between two finite-sample estimators of the same structural
response, distinguished mainly by their bias and variance.

While \textcite{plagborg2021local} locate the divergence at horizons $h > p$, they do not
characterize how local projections actually construct these longer-horizon responses in finite
samples. \textcite{ludwig2026local} closes this gap with an exact least-squares identity that holds
not only in population but in any finite sample. The $h$-step impulse response of an LP($p$) equals
the forward iteration of $h$ one-step predictions from a sequence of VARs of increasing order,
%
\begin{equation}
  \mathrm{IRF}^{\mathrm{LP}(p)}_h(d) =
  \begin{bmatrix} I_K & \mathbf{0} \end{bmatrix}\,
  \Pi(p+h-1)\cdots\Pi(p+1)\,\Pi(p)\,
  \begin{bmatrix} d \\ \mathbf{0} \end{bmatrix},
  \label{eq:ludwig_identity}
\end{equation}
%
where $\Pi(q)$ is the estimated companion matrix of a VAR($q$), $I_K$ is the identity matrix matching
the dimension of the system, and $d$ is the initial structural shock vector.

At $h=1$ the two methods coincide. At $h=2$, however, the LP($p$) is no longer the simple two-step
iterate of a VAR($p$). Instead it advances the one-step forecast with a VAR($p+1$), and each further
horizon effectively adds one lag to the implicit VAR. This identity has profound implications for
model comparison. At equal order, LPs and VARs are neither equally parsimonious nor cast in the same
recursive language. An LP($p$) at horizon $h$ is built from VARs of orders $p, p+1, \dots, p+h-1$,
whereas a standard VAR($p$) holds the order fixed at every step.

The fixed-order VAR($p$) is therefore a heavily restricted special case of the equal-order LP($p$),
which is itself a restricted special case of a highly parameterized VAR($p+h-1$). Seen this way, the
familiar pattern of lower bias but higher variance for LPs relative to a same-order VAR is largely a
mechanical consequence of comparing a more flexible, over-parameterized specification with its own
restriction, rather than an intrinsic property of the projection method. This confounds the standard
reading of the bias-variance trade-off, because at equal lag orders the methodological effect
(LP vs.\ VAR) cannot be cleanly separated from the complexity effect (more vs.\ fewer effective lags).

\FloatBarrier