% Aarons conclusion
\section{Conclusion}

In this paper, we operationalized the complexity-adjusted benchmarking framework proposed by 
\textcite{ludwig2026local} to re-evaluate the finite-sample performance of Vector 
Autoregressions and Local Projections. By moving away from conventional equal-lag 
comparisons, which conflate estimation mechanics with effective model complexity, our 
baseline simulation demonstrated that a fixed $LP(4)$ estimator operates at a complexity 
level equivalent to a highly parameterized $VAR(q)$ with $q \approx 15$. This shifting 
perspective reveals that the standard point-estimation advantage of low-order VARs under 
correct specification is primarily an artifact of parsimony rather than an intrinsic 
architectural superiority of the iterated method. 

Our extension into functional misspecification via a non-linear lag-quadratic data-generating 
process provided a rigorous finite-sample test of the population equivalence established by 
\textcite{plagborg2021local}. Because the centered quadratic term is approximately orthogonal 
to the linear lag space, the true structural impulse response functions remain nearly 
invariant to the strength of the nonlinearity. Asymptotically ($T = 10,000$), both $LP(4)$ 
and adequately lagged VAR specifications collapse onto this identical best linear approximation, 
confirming that population equivalence survives functional misspecification without an 
asymptotic bias boundary. In finite samples ($T = 250$), however, a stark division emerges 
between point estimation and inference. In point estimation, the $VAR(4)$ preserves its strict 
mean squared error dominance over $LP(4)$ because the direct, horizon-by-horizon regressions of 
the local projection propagate sampling noise independently, resulting in a substantially 
larger variance footprint. 

Conversely, the ranking reverses when evaluating inferential validity. The unmodeled quadratic 
state variables inject conditional heteroskedasticity into the projection residuals. Because 
standard VAR confidence intervals rely on the homoskedastic delta method, their analytical 
standard errors systematically understate the true empirical sampling dispersion, leading to 
severe under-coverage that exacerbates with increasing persistence and nonlinearity strength. 
Local projections, by leveraging heteroskedasticity-robust standard errors by default, maintain 
stable, near-nominal 95\% coverage across all examined horizons and persistence regimes. This 
crucial divergence underscores a broader econometric lesson. Estimand equivalence in population 
does not imply inferential equivalence in finite samples. The choice between these two 
approaches is thus inherently objective-dependent, balancing the parametric efficiency of the 
VAR point estimate against the robust interval validity of the direct projection method.

Despite the robust insights gained, our simulation study is subject to several notable 
methodological limitations that clear the path for future research. 

First, our complexity-adjusted benchmarking design imposes strict constraints on the available 
sample size space. Because evaluating the full VAR frontier requires estimating highly 
parameterized systems up to a $VAR(23)$ specification, pushing the sample size below the empirical median of $T = 100$ (or $T = 240$ in the non-linear extension) is computationally unfeasible. Doing so would rapidly exhaust degrees of freedom, rendering the high-order companion matrices rank-deficient and the resulting OLS estimates numerically unstable. Consequently, we are structurally unable to explore small macro-samples, precisely the territory where the finite-sample bias-variance trade-off is most aggressive and where the localized robustness of LPs against dynamic or functional distortions might yield a tangible MSE advantage over tightly restricted VARs.

Second, the introduction of non-linear polynomial terms in lagged state variables inherently destabilizes the simulated systems. The quadratic terms drastically elevate the risk of generating explosive or non-stationary paths during the Monte Carlo replications, particularly when the underlying linear dynamics are highly persistent. To preserve covariance stationarity and ensure a well-defined linear projection estimand, we were forced to restrict the persistence parameter space in the non-linear extension to $\rho \in \{0.5, 0.7\}$, leaving the boundary region near the unit root ($\rho = 0.95$) unexamined. This represents a meaningful omission, as the interaction between high persistence and functional misspecification is precisely where inferential fragility is expected to be most pronounced.

Third, our analysis exposes a structural caveat regarding the found supremacy of local projections in inference. The failure of the VAR intervals is not an unfixable flaw of the iterated architecture itself, but rather a limitation of the default homoskedastic delta-method specification used in standard applied workflows. If the VAR sweep were to be systematically equipped with robust or wild bootstrap standard errors capable of accommodating residual conditional heteroskedasticity, the inferential gap between the two estimators would likely diminish. 

Future research should therefore aim to extend the complexity-adjusted frontier to alternative non-linear frameworks that allow for high persistence without entering explosive regimes. Additionally, formalizing a complexity adjustment for bootstrap-based inference procedures would provide a cleaner horse race, isolating whether the local projection's robust coverage is an intrinsic virtue of direct multi-step forecasting or merely a mechanical benefit of heteroskedasticity-robust variance estimators.